Measuring Directionality in Double Beta Decay and Neutrino Interactions with Kiloton-Scale Scintillation Detectors

### 2013-07-18 Direction.tex
Improved captions. --Lindley

        \subfigure[Default simulation.]{\includegraphics[scale=0.295]{graphs/6p5Meter_5MeVElectrons_Bialkali_KamlandScintSpec_TIME.pdf}}
        \subfigure[Increased TTS (1.28~ns).]{\includegraphics[scale=0.295]{graphs/6p5Meter_5MeVElectrons_Bialkali_KamlandScintSpec_1p28nsTTS_TIME.pdf}}
        \subfigure[Red-sensitive photocathode.]{\includegraphics[scale=0.295]{graphs/6p5Meter_5MeVElectrons_RedSensitiveQE_KamlandScintSpec_TIME.pdf}}
        \caption[]{PE times after TTS application for the simulation of 1000 electrons (5~MeV) with different settings. PEs from Cerenkov light (black) and scintillation light (grey) are compared. The dashed vertical line illustrates a time cut at 34~ns. (a) Default simulation including bialkali photocathode and TTS = 0.1~ns ($\sigma$). The number of PEs per event after the 34.0~ns time cut is 171 from scintillation and 108 from Cerenkov. (b) Default simulation settings but for TTS = 1.28~ns (KamLAND 17 in. PMTs). The number of PEs per event after the 34.0~ns time cut is 349 from scintillation and 88 from Cerenkov. (c) Default simulation settings but for GaAsP photocathode. The number of PEs per event after the 34.0~ns time cut is 50.8 from scintillation and 171 from Cerenkov. \label{time_plots_comparison}}

@@

First we discuss the default simulation settings which are described in the previous section. Figure \ref{time_plot_comparison} (a) shows the TTS-smeared photoelectron detection time for 1000 simulated electrons with 5~MeV energy in the center of the detector with initial momentum direction coinciding with the x-axis. The photoelectrons induced by Cerenkov light arrive earlier, as expected due to the instantaneous emission and the differences in the photon speed. There is however overlap with the PE time distribution coming from scintillation light. In order to compare simulations with different parameters to each other a fixed time cut $t \leq$ 34.0~ns (or 33.0~ns?) is applied (using the truth information of the electron starting time) instead of an event-by-event time reconstruction (see Section \ref{reconstruction_sec} for reconstruction results). For the default simulation case, the number of PEs per event coming from Cerenkov light after the 34.0~ns time cut (108) is 98~\% of the total number of PEs from Cerenkov light (110). For scintillation the number of PEs after the time cut (171) is only 3.2~\% of the total scintillation-induced PEs (5445).  
\begin{figure}[bt]
        \begin{center}
        \includegraphics[scale=0.40]{graphs/cos_psi_comp_h.pdf}
        \caption[]{Angular distribution of photoelectron hits relative to the original electron direction for 1000 events (5~MeV electrons). Default simulation settings were used. A 33.0~ns time cut (black) is compared with a 34.0~ns time cut (red). \label{cerenkov_cone}}
        \end{center}
\end{figure}

>>>>

        \subfigure[ Default simulation.]{\includegraphics[scale=0.295]{graphs/6p5Meter_5MeVElectrons_Bialkali_KamlandScintSpec_TIME.pdf}}
        \subfigure[ Increased TTS (1.28~ns).]{\includegraphics[scale=0.295]{graphs/6p5Meter_5MeVElectrons_Bialkali_KamlandScintSpec_1p28nsTTS_TIME.pdf}}
        \subfigure[ Red-sensitive photocathode.]{\includegraphics[scale=0.295]{graphs/6p5Meter_5MeVElectrons_RedSensitiveQE_KamlandScintSpec_TIME.pdf}}
        \caption[]{PE times after TTS application for the simulation of 1000 electrons (5~MeV) with different settings. PEs from Cerenkov light (black) and scintillation light (grey) are compared. The dashed vertical line illustrates a time cut at 34~ns. (a) Default simulation: bialkali photocathode and TTS = 0.1~ns ($\sigma$). The number of PEs per event after the 34.0~ns time cut is 171 from scintillation and 108 from Cerenkov. (b) Default simulation settings but for TTS = 1.28~ns (KamLAND 17 in. PMTs). The number of PEs per event after the 34.0~ns time cut is 349 from scintillation and 88 from Cerenkov. (c) Default simulation settings but for GaAsP photocathode. The number of PEs per event after the 34.0~ns time cut is 50.8 from scintillation and 171 from Cerenkov. \label{time_plots_comparison}}

@@

First we discuss the default simulation settings which are described in the previous section. Figure \ref{time_plot_comparison} (a) shows the TTS-smeared photoelectron detection time for 1000 simulated electrons with 5~MeV energy in the center of the detector with initial momentum direction coinciding with the x-axis. The photoelectrons induced by Cerenkov light arrive earlier, as expected due to the instantaneous emission and the differences in the photon speed. There is however overlap with the PE time distribution coming from scintillation light. In order to compare simulations with different parameters to each other a fixed time cut $t \leq$ 34.0~ns (or 33.0~ns?) is applied (using the truth information of the electron starting time) instead of an event-by-event time reconstruction (see Section \ref{reconstruction_sec} for reconstruction results). For the default simulation case, the number of PEs per event coming from Cerenkov light after the 34.0~ns time cut (108) is 98~\% of the total number of PEs from Cerenkov light (110). For scintillation the number of PEs after the time cut (171) is only 3.2~\% of the total scintillation-induced PEs (5445).  
\begin{figure}[bt]
        \begin{center}
        \includegraphics[scale=0.40]{graphs/cos_psi_comp_h.pdf}
        \caption[]{Angular distribution of photoelectron hits relative to the original electron direction for 1000 events (5~MeV electrons at the center in x direction): $\cos(\Psi) = x_{hit}/\vec{r}_{hit}$. Default simulation settings were used and both Cerenkov and Scintillation light are included. A 33.0~ns time cut (black) is compared with a 34.0~ns time cut (grey). \label{cerenkov_cone}}
        \end{center}
\end{figure}
